INTELLIGENT SYSTEMS

### 2021-03-28 paper_2.tex
finish 2.4.2

\begin{figure}[htbp]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper2/superpixelsComparison.png}
    \centering
    \caption{Superpixel results from different algorithms. (a) SEEDS. (b) NCuts. (c) SLIC. (d) ERS. (e) LSC.}
    \label{fig: superpixelsComparison}
\end{figure}

@@

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper2/superpixelsComparison.png}
    \centering
    \caption{Superpixel results from different algorithms. (a) SEEDS. (b) NCuts. (c) SLIC. (d) ERS. (e) LSC.}
    \label{fig: superpixelsComparison}
\end{figure}

@@

\subsubsection{Weakly Supervised Semantic Segmentation}
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 0.4 \linewidth]{images/paper2/semanticSegmentation.png}
    \centering
    \caption{Weakly supervised semantic segmentation. (a) A training image with bounding boxes. (b) Output of soft-max layer of $ FCN_c $. (c) Coarse semantic segmentation result. (d) Superpixels with higher probability of foreground. (e) Fore-/Background segmentation result after iterative optimization. (f) Refined semantic segmentation result.}
    \label{fig: flowchartSemanticSegmentation}
\end{figure}
As the title suggests, the LSC algorithm is able to improve semantic segmentation 
with a weakly supervised method. The images of the PASCAL 
VOC2012 database \cite{0781426538} are used as tests, in which there are 1449 images
containing labeled objects and the remaining 10582 images containing only 
bounding boxes used for training and validation. The flow chart of the proposed 
method can be seen in figure (\ref{fig: flowchartSemanticSegmentation}). The steps are as follows: coarse 
semantic segmentation, fore-/background segmentation and refined semantic 
segmentation. In the first step there is a completely convolutional network, 
called $ FCN_c $, trained with images containing only the bounding boxes which 
will be restricted in order to eliminate the border pixels that seem to be 
irrelevant. These new squares are used as positive examples, while the cut 
parts are used as negative examples. For each superpixel \emph{p} generated within 
each bounding box $ i_{th} $, we set $ c_p^i $ as the average value of the colors of each 
pixel within the superpixel and then we set $ l_p^i $ as the label to be estimated (0 
backgroud, 1 foreground). The separation of the background from the 
foreground is seen as an optimization problem
\begin{equation}
    \begin{split}
        \argmax\limits_{l} \sum_i\sum_p(E_a(l_p^i,c_p^i) + \lambda_1E_c(l_p^i, FCN_c)\\
        + \lambda_2\sum_{q\in N(p)}E_s(l_p^i,c_p^i,l_q^i,c_q^i)) 
    \end{split}
\end{equation}
Where $ E_s $ is useful for capturing the smoothness prior produced by a covariance 
matrix, $ E_c $ represents the probability that the superpixel belongs 
to the foreground, while $ E_a $, also called the appearance model, represents 
the probability that a superpixel belongs to the background or foreground. 
After several iterations, which have the purpose of updating the foreground 
and background labels of the superpixels, a correct segmentation will be 
obtained. The segmentation obtained will be used to train a convolutional 
network called $ FCN_r $ which is combined with a dense CRF model useful for 
formulating the final semantic segmentation model. This system is also 
called $ Joint_{sp} $. The model is compared with other supervivided methods \cite{0781426541}, 
a strong one, called \emph{Strong}, and a weak one called \emph{Bbox-seg}, the results of 
which can be seen in figure \ref{fig: semanticSegmentation}.
\begin{figure}[htbp]
    \centering
    \includegraphics[width = 0.6 \linewidth]{images/paper2/segmentationAlgo.png}
    \centering
    \caption{Semantic segmentation. (a) Input image. (b) Strong. (c) Bbox-seg. (d) $ Joint_{sp} $ (LSC) }
    \label{fig: semanticSegmentation}
\end{figure}

While the accuracy, measured with the intersection over-union (\emph{IOU}), 
achieved by the systems mentioned is visible in the table \ref{table accuracy semantic segmentation}.
\begin{table}[h!]
    \centering
    \begin{adjustbox}{max width=\textwidth}
    \begin{tabular}{*{4}{|c}|}%%{|c|c|c|c|}
        \hline
        Strong & Bbox-seg & $ Joint_{sp} $ \\
        \hline
        62.5 & 60.6 & \bfseries{64.0} \\
        \hline
    \end{tabular}
    \end{adjustbox}
    \caption{Semantic segmentation accuracy in terms of Mean IOU (\%)}
    \label{table accuracy semantic segmentation}
\end{table}
